Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-06-07 paper-correlations.tex
l2

High-level algorithm:
\begin{enumerate}
  \item Chose a set of directions
  \item for a direction in the set
    \begin{enumerate}
      \item align the image along the direction
      \item scan the aligned image
    \end{enumerate}
\end{enumerate}

Align and rotate - simple operations with linear computational complexity.
Therefore, the complexity of the entire algorithm depends linearly 
on the number of directions and on the size of the image.

@@

>>>>

Since the method for calculating $l_2$ using the FFT is unknown,
we use the direct approach:
scan the image in each selected direction.
\textcolor{red}{[czech paper]} uses this method,
but our approach saves porosity when rotating the image.
The top-level algorithm is described below, 
and the details are placed in the appendix.

\begin{algorithmic}[1]
  \Procedure{l2\_map}{$a, periodic, directions$}
    \ForAll{$direction \in directions$}
      \State $rotated \gets rotate(a, direction, periodic)$
      \State $l2[direction] \gets scan\_l2(aligned, periodic)$
    \EndFor
    \State \textbf{return} $l2$
  \EndProcedure
\end{algorithmic}

Align and rotate --- simple operations with linear computational complexity.
Therefore, the complexity of the entire algorithm depends linearly 
on the number of directions and on the size of the image.

@@

\section{Algorithm for image rotation}
\label{rotating}

\begin{algorithmic}[1]
  \Procedure{rotate}{$a, direction, periodic$}
    \ForAll{$slice \in eachslice(a)$}
      \State $shift \gets get\_shift(slice, direction)$
      \State $rotated\_slice \gets circshift(slice, shift)$
      \If{$! periodic$}
        \State $rotated\_slice[end - shift:end] \gets -1$
      \EndIf
    \EndFor
  \State \textbf{return} $rotated$
  \EndProcedure
\end{algorithmic}
